% Use the lineno option to display guide line numbers if required.

\templatetype{pnasresearcharticle} % Choose template
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} %= Template for a one-column mathematics article
% {pnasinvited} %= Template for a PNAS invited submission

\setcounter{secnumdepth}{0}

\input{pre-macros}

\title{\input{title.tex}}

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
\author[a,1]{Atticus Geiger}
\author[b]{Alexandra Carstensen}
\author[b]{Michael C.~Frank}
\author[a]{Christopher Potts}

\affil[a]{Department of Linguistics, Stanford University}
\affil[b]{Department of Psychology, Stanford University}

% Please give the surname of the lead author for the running footer
\leadauthor{Geiger}

% Please add here a significance statement to explain the relevance of your work
\significancestatement{The equality relation is a key case study for
broader questions of abstract relational reasoning. Earlier work concluded that neural networks are incapable of learning general solutions
to equality-based reasoning tasks, but this claim is in tension with the extraordinary recent
success of neural networks in artificial intelligence. We resolve this tension
by demonstrating these previous negative results hold only when neural networks are
provided hand-crafted feature representations. When neural networks are instead provided the \newatticus{random or pretrained}
 representations that are now the norm in state-of-the-art work,
 these models easily learn general solutions to equality-based reasoning tasks,
 suggesting that essential aspects of symbolic reasoning can emerge from non-symbolic learning processes.}

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{All four authors contributed to writing the paper and experimental design. Atticus Geiger and Chris Potts wrote the code that was used to run the experiments.}
\authordeclaration{The authors declare no conflicts of interest.}
% \equalauthors{\textsuperscript{1}A.O.(Author One) and A.T. (Author Two) contributed equally to this work (remove if not applicable).}
\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: atticusg@stanford.edu}

% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
\keywords{relational reasoning $|$ neural networks $|$ generalization}

\begin{abstract}
  \input{abstract.tex}
\end{abstract}

\dates{This manuscript was compiled on \today}
\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}

\begin{document}

\maketitle
\thispagestyle{firststyle}
\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}

% If your first paragraph (i.e. with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation. If this is the case, add \parshape=0 to the end of the list environment.

% \section{Introduction}\label{sec:introduction}
